Building socket-aware BPF programs

### 2018-10-27 paper/paper.tex
paper: Add structures listings

@@

The following considerations were made for implementing the lookup helpers. The
consideration of each of these items reflects the definition of the lookup
helpers in Listing~\ref{lst:helper-api}.

@@

\todo{Span this listing across two columns}
\begin{lstlisting}[caption={BPF API helper functions for socket lookup},language=c,label=lst:helper-api,breaklines=true]
struct bpf_sock *bpf_sk_lookup_tcp(void *ctx, struct bpf_sock_tuple *tuple, u32 tuple_size,
                                   u32 netns, u64 flags)
struct bpf_sock *bpf_sk_lookup_udp(void *ctx, struct bpf_sock_tuple *tuple, u32 tuple_size,
                                   u32 netns, u64 flags)
int bpf_sk_release(struct bpf_sock *sk)
\end{lstlisting}

>>>>

\begin{filecontents*}{sk-lookup-api.c}
\import{sk-lookup-api.c}
\end{filecontents*}
\begin{filecontents*}{sk-lookup-structures.c}
\import{sk-lookup-structures.c}
\end{filecontents*}

@@

The following considerations were made for implementing the lookup helpers. The
consideration of each of these items reflects the definition of the lookup
helpers in Listing~\ref{lst:helper-api} and the structure definitions in
Listing~\ref{lst:helper-struct}.

@@

\lstinputlisting[float=*b,%
  caption={BPF API helper functions for socket lookup},%
  language=c,%
  label=lst:helper-api,%
  breaklines=true]{sk-lookup-api.c}

\lstinputlisting[float=*b,%
  caption={BPF API structures for socket lookup (Linux v4.20)},%
  language=c,%
  label=lst:helper-struct,%
  breaklines=true]{sk-lookup-structures.c}
